---
title: "finpar tutorial"
author: rOpenGov
date: "`r Sys.Date()`"
output:
  html_document:
    theme: flatly
---
<!--
%\VignetteEngine{knitr::rmarkdown}
%\VignetteIndexEntry{finpar Markdown Vignette}
%\usepackage[utf8]{inputenc}
-->


Parliament of Finland: unofficial API client
===========

This R package provides tools to access Parliament of Finland data
from the unofficial [Kansan Muisti](http://kansanmuisti.fi) API. 

## Available data sources and tools

[Installation](#installation) (Installation)  
[Parliament terms](#terms) (Terms)  
[Person gender](#genders) (Genders)  


## <a name="installation"></a>Installation

Install the development version:

```{r install2, eval=FALSE}
library(devtools)
install_github("ropengov/finpar")
```

Load the library:

```{r test, message=FALSE, warning=FALSE, eval=TRUE}
library(finpar)
```

Set UTF-8 encoding:

```{r locale, eval=FALSE}
Sys.setlocale(locale="UTF-8") 
```

## <a name="terms"></a>Parliament terms

All terms of the Finnish parliament in 1907-2011

```{r finpar1, results='asis'}
all_terms <- term()
# Show the first ones in a table:
kable(head(all_terms))
```

Get a specific term defined by ID  

```{r finpar2}
term_2011 <- term(id=1)  
print(term_2011)
```


## <a name="gender"></a>Genders

Use genderizeR package to estimate gender for first names (note that there might be [some inaccuracies in gender estimation for Finnish names](https://github.com/rOpenGov/finpar/issues/2))

```{r finpargenders}
# devtools::install_github("kalimu/genderizeR")
library(genderizeR)
x <- c("Sauli", "Tarja", "Mauno")
givenNames <- findGivenNames(x, progress = FALSE)
g <- genderize(x, genderDB=givenNames, blacklist=NULL, progress = FALSE)
kable(g)
```

## Related 

 * R code to calculate [co-sponsorship networks from bills (and motions) passed in the Finnish Parliament](https://github.com/briatte/eduskunta/)


## Acknowledgements

R client for the unofficial API of [Parliament of Finland](http://web.eduskunta.fi/Resource.phx/parliament/index.htx) provided by NGO [Kansan Muisti](http://www.kansanmuisti.fi/about/background/). Parliament of Finland does not provide an official API, but Kansan Muisti does provide a RESTful API to a database mostly compiled by scraping data from parliament's web page. Great work !


## Licensing and Citations

This work can be freely used, modified and distributed under the 
[MIT license](http://en.wikipedia.org/wiki/MIT_License).

```{r citation, message=FALSE, eval=TRUE}
citation("finpar")
```

## Session info

This vignette was created with

```{r sessioninfo, message=FALSE, warning=FALSE}
sessionInfo()
```




