---
title: "finpar tutorial"
author: rOpenGov
date: "`r Sys.Date()`"
output:
  html_document:
    theme: flatly
---
<!--
%\VignetteEngine{knitr::rmarkdown}
%\VignetteIndexEntry{finpar Markdown Vignette}
%\usepackage[utf8]{inputenc}
-->


Parliament of Finland: unofficial API client
===========

This R package provides tools to access Parliament of Finland data
from the unofficial [Kansan Muisti](http://kansanmuisti.fi)
2.0 [API](http://kansanmuisti.fi/api/v1/). For API documentation,
check [here](http://dev.kansanmuisti.fi/static/api_v1_doc/index.html).


## Installation and usage

[Installing the package](#installation) (Installing the package)  
[Gender analysis](#genders) (Estimating genders)  

### Available data sources and tools

The following API endpoints are currently wrapped by `finpar`:

| Data                | API endpoint                       | Function                           |
|---------------------|------------------------------------|------------------------------------|
| Parliamentary terms | [http://kansanmuisti.fi/api/v1/term](http://kansanmuisti.fi/static/api_v1_doc/index.html#api-Term) | `term()` |
| Members of the Parliament | [http://kansanmuisti.fi/api/v1/member](http://kansanmuisti.fi/static/api_v1_doc/index.html#api-Member) | `member()` |
| Plenary sessions | [http://kansanmuisti.fi/api/v1/plenary_session](http://kansanmuisti.fi/static/api_v1_doc/index.html#api-Plenary_Session) | `plenary_session()` |


## <a name="installation"></a>Installation

Install the development version:

```{r install2, eval=FALSE}
library(devtools)
install_github("ropengov/finpar")
```

Load the library:

```{r test, message=FALSE, warning=FALSE, eval=TRUE}
library(finpar)
```

Set UTF-8 encoding:

```{r locale, eval=FALSE}
Sys.setlocale(locale="UTF-8") 
```

## <a name="terms"></a>Parliament terms

All terms of the Finnish parliament in 1907-2011

```{r finpar1, results='asis', message=FALSE}
all_terms <- term()
# Show the first ones in a table:
library(knitr)
kable(head(all_terms))
```

Get a specific term defined by ID  

```{r finpar2}
term_2011 <- term(id=1)  
print(term_2011)
```



## <a name="members"></a>Parliament members

Get all parliament members and plot their age distribution

```{r finparmember, results='asis', message=FALSE, fig.width=10, fig.height=7}
all_members <- member()
ages <- sapply(all_members, function (x) {x$age})
hist(ages, col = "gray", xlab = "Age", main = "Age distribution of parliament members", las = 1)
```

Get a specific member defined by ID:

```{r finparmember2}
jorn_donner <- member(id=30)  

# List available variables
print(names(jorn_donner))

# Check age
jorn_donner$age
```


## <a name="members"></a>Plenary sessions

Get all plenary sessions 

```{r plenarysession, results='asis', message=FALSE}
all_plenary_sessions <- plenary_session()
```
  
Get a specific plenary session defined by ID

```{r plenarysession2}
session <- plenary_session(id=30)  

# List available variables
kable(session)
```



## <a name="gender"></a>Genders

Use [genderizeR](https://github.com/kalimu/genderizeR) to estimate gender for first names (note that there might be [some inaccuracies in gender estimation for Finnish names](https://github.com/rOpenGov/finpar/issues/2)):

```{r finpargenders}
# devtools::install_github("kalimu/genderizeR")
library(genderizeR)
x <- c("Sauli", "Tarja", "Mauno")
givenNames <- findGivenNames(x, progress = FALSE)
g <- genderize(x, genderDB=givenNames, blacklist=NULL, progress = FALSE)
kable(g)
```

## Related 

R code to calculate [co-sponsorship networks from bills (and motions) passed in the Finnish Parliament](https://github.com/briatte/eduskunta/) by  François briatte


## Acknowledgements

R client for the unofficial API of [Parliament of Finland](http://web.eduskunta.fi/Resource.phx/parliament/index.htx) provided by NGO [Kansan Muisti](http://www.kansanmuisti.fi/about/background/). Parliament of Finland does not provide an official API, but Kansan Muisti does provide a [RESTful API](http://kansanmuisti.fi/api/v1/) to a database mostly compiled by scraping data from parliament's web page. Great work !


## Licensing and Citations

This work can be freely used, modified and distributed under the 
[MIT license](http://en.wikipedia.org/wiki/MIT_License).

```{r citation, message=FALSE, eval=TRUE}
citation("finpar")
```

## Session info

This vignette was created with

```{r sessioninfo, message=FALSE, warning=FALSE}
sessionInfo()
```




