---
title: "finpar tutorial"
author: rOpenGov
date: "`r Sys.Date()`"
output:
  html_document:
    theme: flatly
---
<!--
%\VignetteEngine{knitr::rmarkdown}
%\VignetteIndexEntry{finpar Markdown Vignette}
%\usepackage[utf8]{inputenc}
-->


Parliament of Finland: unofficial API client
===========

This R package provides tools to access Parliament of Finland data
from the unofficial [Kansan Muisti](http://kansanmuisti.fi) API. 

## Available data sources and tools

[Installation](#installation) (Asennus)  



## <a name="installation"></a>Installation

Install the development version:

```{r install2, eval=FALSE}
library(devtools)
install_github("ropengov/finpar")
```

Load the library:

```{r test, message=FALSE, warning=FALSE, eval=TRUE}
library(finpar)
```

Set UTF-8 encoding:

```{r locale, eval=FALSE}
Sys.setlocale(locale="UTF-8") 
```


## Licensing and Citations

This work can be freely used, modified and distributed under the 
[MIT license](http://en.wikipedia.org/wiki/MIT_License).

```{r citation, message=FALSE, eval=TRUE}
citation("finpar")
```

## Session info

This vignette was created with

```{r sessioninfo, message=FALSE, warning=FALSE}
sessionInfo()
```




